Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-10-09 ms.tex
show the drastic improvement from NFF=512 to NFF=2048

@@

\begin{figure*}
\gridline{
\fig{individual_azlab06_baseline3.pdf}{0.49\textwidth}{Stripe Baseline $2048 \times 256$}\\
\fig{individual_azlab06_sub320_6p0mA}{0.49\textwidth}{Subarray Baseline $320 \times 320$}
}
\gridline{
\fig{individual_azlab06_sub320_6p0mA_t100_110.pdf}{0.49\textwidth}{5-15 min Zoom $320 \times 320$}\\
\fig{individual_azlab06_sub320_6p0mA_t005_t015.pdf}{0.49\textwidth}{100-110 min Zoom $320 \times 320$}
}
\caption{The time series of the AZLab 06 $320 \times 320$ subarray shows considerably higher scatter than the stripe mode.
A zoom-in on the $320 \times 320$ subarray time series shows that it exhibits oscillations every 4 integrations.
}\label{fig:sub320vsStripeBaseline2}
\end{figure*}

>>>>

The subarray time series is very sensitive to the fast-frame resets where the entire array is quickly reset at the beginning of an integration.
These resets are needed to ensure that pixels outside a subarray don't overfill their well capacity and leak into the subarray.
When NFF=512, the fast-frame resets are cycled through 4 different sections of the detector.
This results in a cycling pattern with a period of 4 integrations shown in Figure \ref{fig:sub320vsStripeBaseline2}.
When NFF=2048, there is no cycling pattern shown in Figure \ref{fig:sub320NFF512vs2048}.

@@

\begin{figure*}
\gridline{
\fig{individual_azlab06_baseline3.pdf}{0.49\textwidth}{Stripe Baseline $2048 \times 256$}\\
\fig{individual_azlab06_sub320_6p0mA}{0.49\textwidth}{Subarray Baseline $320 \times 320$}
}
\gridline{
\fig{individual_azlab06_sub320_6p0mA_t100_110.pdf}{0.49\textwidth}{5-15 min Zoom $320 \times 320$}\\
\fig{individual_azlab06_sub320_6p0mA_t005_t015.pdf}{0.49\textwidth}{100-110 min Zoom $320 \times 320$}
}
\caption{The time series of the AZLab 06 $320 \times 320$ subarray shows considerably higher oscillations than the stripe mode.
A zoom-in on the $320 \times 320$ subarray time series shows that it exhibits oscillations every 4 integrations.
NGROUP=10, NINT=1000.
}\label{fig:sub320vsStripeBaseline2}
\end{figure*}

\begin{figure*}
\gridline{
\fig{individual_azlab06_sub320_9p0mA}{0.49\textwidth}{5-8 min Zoom $320 \times 320$ NGROUP=2}
}
\caption{The time series of the AZLab 06 $320 \times 320$ subarray still has oscillations every 4 integrations with NGROUP=2, NINT=3600.
}\label{fig:sub320vsStripeBaseline2}
\end{figure*}

\begin{figure*}
\gridline{
\fig{individual_azlab06_sub320_6p0mA_t005_t015.pdf}{0.49\textwidth}{5-15 min Zoom $320 \times 320$ with NFF=512}\\
\fig{individual_azlab06_sub320_nff2048_t005_t015.pdf}{0.49\textwidth}{5-15 min Zoom $320 \times 320$ with NFF=2048}
}
\caption{The time series of the AZLab 06 $320 \times 320$ subarray is very sensitive tot he fast frame resets.
When NFF=512, the fast frame resets cycle through the $320 \times 320$ subarray every 4 integrations, resulting in a 4-integration cycle.
When NFF=2048, there is no long a pattern and each integration is consistent.
}\label{fig:sub320NFF512vs2048}
\end{figure*}
